% Latex Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.
%
% INSTRUCTIONS:
% pdflatex cv-us.tex

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Gregory Burd}

% Replace this with a link to your CV (as in
% \def\footerlink{http://jblevins.org/projects/cv-template/})
% if you like, or set it empty (as in \def\footerlink{}) to remove
% the link in the footer:

\def\footerlink{http://gregburd.com/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {software, database},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  72 Lexington Ave \\
  Cambridge, MA 02138-3337
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (617) 869-0997 \\
    Email: & \href{mailto:greg@burd.me}{\tt greg@burd.me} \\
  \end{tabular}
\end{minipage}

\vspace{0.25in}

\subsection*{Summary}

\begin{itemize}

\item I am seeking a position as a software engineer/architect or other
  contributing member of an engineering team.

\item My passion is the production and delivery of excellent, elegant and
  purposeful software. I care deeply about the people I work with and the teams
  I contribute to. I am interdisciplinary, unconventional, and ardent. I enjoy
  projects requiring creative problem solving, prudent risk taking, careful
  study and reuse of existing techniques to a thoughtful resolution. I lead or
  follow and when I do take the initiative I accept the responsibility for the
  outcome. I continue to learn from my mistakes.

\end{itemize}


\section*{Current Skills}

\begin{itemize}
\item Software Architecture, Databases, Distributed Systems, C/C++, Erlang,
  Networking, System Administration/Operations, UNIX* (Linux, BSD, OS/X)
\end{itemize}


\section*{Employment}

\begin{itemize}
\item {\it Basho Technologies}, Software Architect and Product Manager -- Cambridge, MA -- Jul 2011 - Present

\begin{itemize}
\item At Basho I am responsible for a clear and shared definition of our
  product direction. Previous to this role I also served as an Software
  Architect and a member of the Client Services team.
\end{itemize}

\item {\it Oracle Corporation, Embedded Global Business Unit (EGBU), Berkeley DB}, Product Manager -- Burlington, MA -- Feb 2006 - Mar 2011

\begin{itemize}
\item Post-acquisition, I was responsible for educating Oracle Marketing and
  Sales about Berkeley DB.  I worked to transition our documentation into
  Oracle's Documentation Group.  I worked with Oracle Legal to verify and
  classify Berkeley DB's intellectual property properly.  I worked with the
  contracts team on product language for many new customer contracts.  I
  defined product direction for Berkeley DB.  I spawned, and owned start to
  finish the integration of Berkeley DB and SQLite as a replacement for Oracle
  Lite and a partnership between Oracle and Hwaci. I helped to define the
  Oracle NoSQL Database product.
\end{itemize}

\item {\it Sleepycat Software}, Software Engineer/Product Manager -- Boston, MA -- Jul 2002 - Feb 2006

\begin{itemize}
\item I authored a set of macros similar to queue.h that worked cross process
  in shared memory called shqueue.h now used in many products and operating
  systems.  I defined the product roadmap, visited customers, produced SWOT and
  competitive analysis documents, attended analyst meetings, wrote white papers
  and generated web content.
\end{itemize}

\item {\it KnowNow, a Kleiner Perkins start-up}, Technical Alliance Manager -- Menlo Park, CA -- Dec 2000 - Jun 2002

\begin{itemize}
\item I was the technical person working with the executive, sales and
  marketing teams during the product definition phase within the KP incubator
  offices. My market analysis led to the development of a MS Excel/KnowNow
  event integration layer allowing real-time notification between the browser,
  databases and spreadsheets.  I developed the Ruby KnowNow client library.  I
  developed some of the Python-server and contributed to the design of the
  KnowNow Event Notification Server.  I developed alliances with Accenture, HP
  and other strategic integrators.  I educated their teams, provided support
  and helped them to deliver solutions to their customers.
\end{itemize}

\item {\it Primix Solutions}, Managing Consultant -- Watertown, MA -- Sep 1996 - Jun 1999

\begin{itemize}
\item I wrote code and contributed to the design of many customer web-sites.  I
  helped build reusable components and fostered the early stage development of
  Tapestry (http://tapestry.apache.org/).  I wrote the database schema,
  optimized Sun hardware, integrated Veritas for backup and configured Solaris
  2.7 for this deployment.
\end{itemize}

\item {\it Sun Microsystems}, Member of Technical Staff (MTS-4) Software Engineer -- Bay Area, CA -- Jul 1999 - Nov 2000
I worked in a number of areas within Sun: ???
\begin{itemize}
\item I wrote code for the Desktop Technologies {\it OpenStep for Solaris}
  team.  I identified and fixed bugs in the Objective-C to C++ compiler, within
  Adobe's Display PostScript engine and deep in Solaris' threads library while
  porting various OpenStep applications to Solaris 2.7.
\item I joined JavaSoft in the {\it Java Applications Group} where I wrote code
  for various applications.  I was the engineering lead for a team of five
  engineers building JavaSafe, a software source code management (SCM) GUI and
  server loosely based on CVS that shipped commercially.
\item I joined the {\it Market Development Engineering (MDE)} in the Broomfield
  office where I worked with many of Sun's most strategic RDBMS and ERP
  partners (Informix, Oracle, Sybase, PeopleSoft).  I kept in contact with
  partners and frequently debugged their code.  I sponsored these fixes into
  Sun Engineering and provide code to work-around issues until the fixes were
  released.
\end{itemize}

\item {\it Marble Associates}, Managing Associate Consultant -- San Jose, CA then later Watertown, MA -- Aug 1993 - Aug 1996

\begin{itemize}
\item I wrote code in Objective-C/NeXTSTEP on-customer site in support of their
  business process reengineering efforts. I designed and authored many desktop
  applications, the relational database schema that they connected to and even
  an object-to-relational mapping (ORM) layer.  I wrote SBIR grant proposals
  and I implemented the software for those which were approved.  I co-authored
  and deployed one of the first ever web-applications that used the
  WorldWideWeb.app, the CERN HTTPD server and a Sybase database to generate
  dynamic HTML.
\end{itemize}

\item {\it NeXT Computer}, Developer Support Team -- Redwood City, CA -- May 1992 - Sep 1992

\begin{itemize}
\item I wrote code, fixed bugs and investigated issues for strategic partners.
  I was responsible for the ISDN Kit (TCP/IP over ISDN links), Renderman (the
  3D graphics language behind Pixar) and general issues with the AppKit (GUI).
\end{itemize}

\end{itemize}


\section*{Education}

\begin{itemize}
  \item BS/CS, New Mexico State University, 1991-1992

  \item BA/MA, Whitter College, 1990-1991
    In a 3/2 program with UCLA for a masters of photojournalism.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
